Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
brushing up.

TBD: code block cannot show results. properties should be distinguished from examples.

TBD: Haddock version 2.7.2 or earlier does not provide annotation syntax
for examples and properties.

@@

We implemented the {\tt >>>} syntax and it
is available in Haddock version 2.8 or later.
We also extended Haddock to support the {\tt prop>} syntax
which will be available in the future release.
Both examples and properties in Haddock annotation are pretty printed when producing document
such as in HTML.

>>>>

\noindent Though the code block itslef is a necessary feature,
we think this kind usage has problems.
If the equations above are examples, we cannot distinguish
their results from their expression to be evaluated.
If they are properties, they should be distinguished
from example code.

@@

As we described, Haddock version 2.7.2 or earlier has
anotation syntax for code block but does not provide
annotation syntax for examples and properties.
We implemented annotation syntax for examples ({\tt >>>}) and 
it is available in Haddock version 2.8 or later.
We also extended Haddock to support annotation syntax for
properties ({\tt prop>})
which will be available in the future release.
Both examples and properties in Haddock annotation are pretty printed when producing document
such as in HTML.
